TODO Title

### 2013-03-11 CGP Journal/main.tex
Added outline of CGP journal paper, removed windows line endings

>>>>

\section{Cartesian Genetic Programming}

\section{Duplicate Evaluation Avoidance}

\subsection{Skip}

\subsection{Accumulate}

\subsection{Single}

\section{Genome Ordering}

\subsection{Reorder}

\subsection{DAG}

\section{Qualitative Comparisons}

TODO All possible combinations of Skip, Accumulate, Single, with Normal, Reorder, Dag.

\subsection{Problem Set}
TODO 3-bit Parity, 6-bit Multiply, 4-16-bit Decode, 16-4-bit Encode

TODO Consider adding 5-bit Parity or Equality

\subsection{Parameter Setting}
TODO Mutation Rate / Genome Size grid

TODO Method for choosing parameter values.

\subsection{Results}
TODO Compare using a table the best parameters found for each configuration.
One table per problem.

\subsection{Generalization}
TODO Consider dropping this section due to computational limits.

\section{Analysis of Evolutionary Mechanisms}
TODO Explain footprint concept here.
\subsection{Inactive Nodes and Node Duplication}
TODO Look at how much of the genome is duplicated in both active and inactive

TODO Look at how much of the genome is unused.

\subsection{Node Reactivation and Active Node Mutation}
TODO For each node that was active, then inactive, then active again, see how its changed.

TODO For each node that is active, look at how successful mutations change its behavior.

\subsection{Source of High Variance}
TODO Look for general indicators of high evaluation runs.

TODO Look for footprint moving.

TODO Look for active node clustering.

TODO Look into how often children replace parents.

\section{Conclusions}
